A Simple and Strong Baseline for Universal Targeted Attacks on Siamese Visual Tracking

### 2021-07-12 博士/论文提交/adversarial_attack/TCSVT/latex/main.tex
把与最好方法的比较分成有目标攻击的比较和无目标攻击的比较。

\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.48\textwidth]{images_imperceptible/SOTA.png}
  \end{center}
  \caption{Precision score with respect to the \textit{real trajectory} on OTB2015.}
  \label{fig:SOTA}
\end{figure}

We compare the attack method proposed in this paper with the latest attack methods, including the AlexNet-based untargeted attack method CSA \cite{CSA}, and two other targeted attack methods: the AlexNet-based FAN \cite{FAN} and the ResNet50-based TTP \cite{TTP} (Figure \ref{fig:SOTA}). We report the accuracy scores with respect to the real/fake trajectories in Table \ref{tab:SOTA}. CSA \cite{CSA} is a Siamese tracking attack method called cooling-shrinking attack. CSA can suppress the peak region on the heat map reflecting the target location, which is used to attack the tracker's targeting ability. CSA can also simultaneously force the tracker's predicted bounding box to shrink, which is used to attack the bounding box regression capability of the tracker. However, this method requires running a generative network for each frame to obtain adversarial information, so the attack time is as high as 4720 ms, making it difficult to meet the demand for real-time tracking. CSA reduces the accuracy score with respect to the real trajectory from 0.851 to 0.458. Due to the limitations of the algorithm design, CSA cannot perform targeted attacks for Siamese trackers. Recently, Liang et al. proposed a fast attack network (FAN) \cite{FAN} for attacking SiamFC trackers. To perform untargeted attacks, FAN proposes a drift loss that shifts the tracker's prediction of the target's position. The tracking error accumulates over time until the tracker loses the target completely. To perform targeted attacks, FAN proposes embedding feature loss for improving the similarity between the features of the adversarial sample and the features of regions specified by a particular trajectory. FAN can reduce the accuracy score with respect to the real trajectory from 0.720 to 0.180. However, the accuracy score with respect to fake trajectories is only 0.420. Similar to SCA, FAN also requires running a generative network for each frame to obtain adversarial information. Nakka et al. \cite{TTP} proposed the temporally transferable perturbations (TTP) for attacking the SiamRPN++ tracker. TTP generates a single adversarial perturbation from the template image and adds this perturbation to each search image of the video. TTP reduces the accuracy score with respect to the real trajectory from 0.910 to 0.080, which is effective for untargeted attacks. However, the accuracy score with respect to the fake trajectory is only 0.692, which demonstrates that TTP's performance of targeted attacks is limited. In addition, this method needs to run a generative network for each video to obtain adversarial information, thus requires the computational and storage resources of the object tracking platform, which makes it difficult to deploy the method to resource-constrained platforms. Our method can reduce the accuracy score with respect to real trajectories from 0.861 to 0.092. The accuracy score is up to 0.795 with respect to fake trajectories, which is significantly better than other methods, and only needs to perform the add operation to generate adversarial information for any video without gradient optimization or network inference.

>>>>

% \begin{figure}[t]
%   \begin{center}
%     \includegraphics[width=0.48\textwidth]{images_imperceptible/SOTA.png}
%   \end{center}
%   \caption{Precision score with respect to the \textit{real trajectory} on OTB2015.}
%   \label{fig:SOTA}
% \end{figure}

We compare the attack method proposed in this paper with the latest attack methods, including CSA \cite{CSA}, RTAA \cite{RTAA}, SPARK \cite{SPARK}, FAN \cite{FAN} and TTP \cite{TTP}. We report the untargeted attack result (Table \ref{tab:SOTA}) and the targeted attack result (Table \ref{tab:SOTA1}) on OTB2015. CSA \cite{CSA} is a Siamese tracking attack method called cooling-shrinking attack. CSA can suppress the peak region on the heat map reflecting the target location, which is used to attack the tracker's targeting ability. CSA can also simultaneously force the tracker's predicted bounding box to shrink, which is used to attack the bounding box regression capability of the tracker. However, this method requires running a generative network for each frame to obtain adversarial information, so the attack time is as high as 4720 ms, making it difficult to meet the demand for real-time tracking. CSA reduces the accuracy score with respect to the real trajectory from 0.851 to 0.458. Due to the limitations of the algorithm design, CSA cannot perform targeted attacks for Siamese trackers. Recently, Liang et al. proposed a fast attack network (FAN) \cite{FAN} for attacking SiamFC trackers. To perform untargeted attacks, FAN proposes a drift loss that shifts the tracker's prediction of the target's position. The tracking error accumulates over time until the tracker loses the target completely. To perform targeted attacks, FAN proposes embedding feature loss for improving the similarity between the features of the adversarial sample and the features of regions specified by a particular trajectory. FAN can reduce the accuracy score with respect to the real trajectory from 0.720 to 0.180. However, the accuracy score with respect to fake trajectories is only 0.420. Similar to SCA, FAN also requires running a generative network for each frame to obtain adversarial information. Nakka et al. \cite{TTP} proposed the temporally transferable perturbations (TTP) for attacking the SiamRPN++ tracker. TTP generates a single adversarial perturbation from the template image and adds this perturbation to each search image of the video. TTP reduces the accuracy score with respect to the real trajectory from 0.910 to 0.080, which is effective for untargeted attacks. However, the accuracy score with respect to the fake trajectory is only 0.692, which demonstrates that TTP's performance of targeted attacks is limited. In addition, this method needs to run a generative network for each video to obtain adversarial information, thus requires the computational and storage resources of the object tracking platform, which makes it difficult to deploy the method to resource-constrained platforms. Our method can reduce the accuracy score with respect to real trajectories from 0.861 to 0.092. The accuracy score is up to 0.795 with respect to fake trajectories, which is significantly better than other methods, and only needs to perform the add operation to generate adversarial information for any video without gradient optimization or network inference.
